---
title: "ElectionForecasting"
author: "Saurabh"
date: "5/18/2020"
output: html_document
---


# The Dataset
Data from RealClearPolitics.com
• Instances represent a state in a given election
• State: Name of state
• Year: Election year (2004, 2008, 2012)
• Dependent variable
• Republican: 1 if Republican won state, 0 if Democrat won
• Independent variables
• Rasmussen, SurveyUSA: Polled R% - Polled D%
• DiffCount: Polls with R winner – Polls with D winner
• PropR: Polls with R winner / # polls 

##Load Libraries
```{r}
library(tidyverse)
library(mice)
```

## Data Loading 
```{r}
polling <-  read_csv("PollingData.csv")
str(polling)
table(polling$Year)
summary(polling)
```


## Missing Data Imputation
```{r}
set.seed(144)
imputed = complete(mice(polling))

summary(imputed)

polling <- polling %>% 
          mutate(Rasmussen = imputed$Rasmussen ,
                  SurveyUSA = imputed$SurveyUSA)%>%
          glimpse()

summary(polling)

```

## Create Training & Testing Set
```{r}

train <- filter(polling , Year == 2004 | Year == 2008)
test <- filter(polling , Year == 2012)
```


```{r}
table(train$Republican)


table(sign(train$Rasmussen))


table(train$Republican , sign(train$Rasmussen))

cor(train %>% select(.,-"State"))

```


## Modeling 
### Single Var model
```{r}
m1 <- glm(Republican ~ PropR , data= train , family = "binomial")
summary(m1)

pred1 <- predict(m1 , type = "response")
table(train$Republican ,pred1 >= 0.5)
```

### 2 var model
```{r}
m2 <- glm(Republican ~ SurveyUSA +DiffCount, data = train , family = "binomial")
summary(m2)

pred2 <- predict(m2 , type ="response")
table(train$Republican , pred2 >= 0.5)
```

### Applying pred to test set
```{r}
table(test$Republican , sign(test$Rasmussen))


TestPrediction = predict(m2, newdata = test , type ="response")
table(test$Republican , TestPrediction >= 0.5)
```

### Looking at the incorrect prediction
```{r}
test %>% filter(TestPrediction >= 0.5 , Republican == 0)
```

Here's where Obama won from!
