---
title: "Emails_Recitaion"
author: "Saurabh"
date: "5/21/2020"
output: html_document
---

### Load the libraries
```{r}
library(tm)
library(rpart)
library(rpart.plot)
library(caTools)
library(ROCR)
```


## Read the data
```{r}
emails = read.csv("energy_bids.csv" , stringsAsFactors =FALSE)
str(emails)


```
We have 2 vars : email and whether it is responsive

Lets look at a mail and whether it is responsive ?
```{r}
emails$email[1]
emails$responsive[1]
```

this mail isn't responsive.
Lets find out how many mails are :
```{r}
table(emails$responsive)
```

We can see that only 139 are.


## Pre-processing

Create corpus :
```{r}
corpus = Corpus(VectorSource(emails$email))
corpus[[1]]$content
```

Apply operations : 
```{r}
corpus = tm_map(corpus , tolower)
corpus = tm_map(corpus , removePunctuation)
corpus = tm_map(corpus , removeWords , stopwords("english"))
corpus = tm_map(corpus , stemDocument)
```

View 1st email :
```{r}
corpus[[1]]$content
```

Now corpus is ready for ml algos.

##
Create matrix
```{r}
dtm = DocumentTermMatrix(corpus)
dtm
```

Remove Sparse terms
```{r}
dtm = removeSparseTerms(dtm , 0.97)
dtm
```

Convert to df
```{r}
labeledTerms = as.data.frame(as.matrix(dtm))
```

Add outcome var
```{r}
labeledTerms$responsive = emails$responsive
str(labeledTerms)
```


## Split Data
```{r}
set.seed(144)
split = sample.split(labeledTerms$responsive , SplitRatio = 0.7)
train = subset(labeledTerms , split == TRUE)
test = subset(labeledTerms , split == FALSE)
```

## CART model
```{r}
emailcart = rpart(responsive ~ . , data =train ,method = "class")
prp(emailcart)
```

## Evaluate

Make predictions on test set
```{r}
pred = predict(emailcart , newdata = test)
pred[1:10,]

```

Extract the prob of mail being responsive
```{r}
pred.prob = pred[,2]
```

Compute accuracy
```{r}
table(test$responsive , pred.prob >= 0.5)
```

```{r}
(195+25)/(195+20+17+25)
```

Since Baseline always predicts as non responsive , check cart against it.

```{r}
table(test$responsive)
```

Accurcay of BL : 
```{r}
215/257
```

So CART model has slightly better accuracy.

## Roc Curve
```{r}
predRocr = prediction(pred.prob , test$responsive)
perfRocr =performance(predRocr , "tpr" , "fpr")
plot(perfRocr , colorize = TRUE)
```

## Compute Auc
```{r}
performance(predRocr , "auc")@y.values
```

Our model can predict responsive mails with an accuracy of 80%