---
title: "Framingham Heart Study"
author: "Saurabh"
date: "5/13/2020"
output: html_document
---

Framingham Heart study dataset includes several demographic risk factors:-
sex: male or female;
age: age of the patient;
education: levels coded 1 for some high school, 2 for a high school diploma or GED, 3 for some college or vocational school, and 4 for a college degree.

The data set also includes behavioral risk factors associated with smoking
currentSmoker: whether or not the patient is a current smoker
cigsPerDay: the number of cigarettes that the person smoked on average in one day.

Medical history risk factors
BPMeds: whether or not the patient was on blood pressure medication
prevalentStroke: whether or not the patient had previously had a stroke
prevalentHyp: whether or not the patient was hypertensive
diabetes: whether or not the patient had diabetes

Risk factors from the first physical examination of the patient.

totChol: total cholesterol level
sysBP: systolic blood pressure
diaBP: diastolic blood pressure
BMI: Body Mass Index
heartRate: heart rate
glucose: glucose level
TenYearCHD: 10 year risk of coronary heart disease CHD


## Libraries

```{r}
library(tidyverse)
library(tidymodels)
library(caTools)
library(ROCR)
```


## Get Data
```{r}
framingham <- read_csv("framingham.csv")
```

```{r}
glimpse(framingham)
str(framingham)
```
```{r}
head(framingham)
```

```{r}
summary(framingham)
```



## Split Train & Test
```{r}
set.seed(1000)
split = sample.split(framingham$TenYearCHD, SplitRatio = 0.65)
train = subset(framingham, split==TRUE)
test = subset(framingham, split==FALSE)
```



```{r}
framinghamLog = glm(TenYearCHD ~ ., data = train, family=binomial)
summary(framinghamLog)
```
If we look at the summary of the model, we can see that education, currentSmoker, BPMeds,diabetes, diaBP, BMI, heartRate are not significant in this model.




Predictions on the test set
```{r}
predictTest = predict(framinghamLog, type="response", newdata=test)

```

We can find the accuracy of the model using confusion matrix

Confusion matrix with threshold of 0.5
```{r}
table(test$TenYearCHD, predictTest > 0.5)

```

Accuracy

```{r}
(1069+11)/(1069+6+187+11)

```



Improved Logistic Regression Model

```{r}
framinghamLog=glm(TenYearCHD ~ .-education-currentSmoker-BMI-diaBP, data = train, family=binomial)
summary(framinghamLog)
```


Predictions on the test set

```{r}
predictTest = predict(framinghamLog, type="response", newdata=test)

```

We can find the accuracy of the model using confusion matrix

Confusion matrix with threshold of 0.5

```{r}
table(test$TenYearCHD, predictTest > 0.5)

```


Accuracy
```{r}
(1102+12)/(1102+12+6+187)
```

For this model the accuracy of this model is slightly greater than our previous model.