---
title: "SupremeCourt"
author: "Saurabh"
date: "5/18/2020"
output: html_document
---

## Data

Cases from 1994 through 2001
• In this period, same nine justices presided SCOTUS
• Breyer, Ginsburg, Kennedy, O’Connor, Rehnquist (Chief
Justice), Scalia, Souter, Stevens, Thomas
• Rare data set – longest period of time with the same set
of justices in over 180 years
• We will focus on predicting Justice Stevens’ decisions
• Started out moderate, but became more liberal
• Self-proclaimmed conservative 

## Variables
• Dependent Variable: Did Justice Stevens vote to reverse
the lower court decision? 1 = reverse, 0 = affirm
• Independent Variables: Properties of the case
• Circuit court of origin (1st – 11th, DC, FED)
• Issue area of case (e.g., civil rights, federal taxation)
• Type of petitioner, type of respondent (e.g., US, an employer)
• Ideological direction of lower court decision (conservative or
liberal)
• Whether petitioner argued that a law/practice was
unconstitutional 


## Load Libraries
```{r}
library(tidyverse)
library(rpart)
library(rpart.plot)
library(ROCR)
library(caTools)
library(e1071)
library(caret)
library(randomForest)
```

## Load Data
```{r}
stevens <- read_csv("stevens.csv")
glimpse(stevens)
str(stevens)
```


## Split 
```{r}
set.seed(3000)
spl <- sample.split(stevens$Reverse , SplitRatio = 0.7)

train <- subset(stevens , spl == TRUE)
test <- subset(stevens , spl == FALSE)
```


## Cart Model
```{r}
stree <- rpart(Reverse ~ Circuit + Issue + Petitioner + Respondent +LowerCourt + 
                 Unconst , data = train , 
               method =  "class" , minbucket = 25)
prp(stree)
```
###predict
```{r}
predictCart <- predict(stree , newdata = test ,type = "class")
table(test$Reverse , predictCart)

```


##ROC
```{r}
predictRoc <- predict(stree , newdata = test)
predictRoc

pred = prediction(predictRoc[,2], test$Reverse)
perf = performance(pred , "tpr" , "fpr")
plot(perf)
```
###Accuracy 
```{r}
(41+71) / (41+36+22+71)
```

##Random Forest
```{r}
sforest <- randomForest(Reverse ~ Circuit + Issue + Petitioner + Respondent +LowerCourt + 
Unconst , data = train , nodesize =  25 , ntree = 200)

train <- train %>% mutate(Reverse = as.factor(Reverse))
test <- test %>% mutate(Reverse = as.factor(Reverse))

sforest <- randomForest(Reverse ~ Circuit + Issue + Petitioner + Respondent +LowerCourt + 
          Unconst , data = train , nodesize =  25 , ntree = 200)

predictforest <- predict(sforest , newdata = test)

table(test$Reverse , predictforest)
```
### Accuracy
```{r}
(53+71) / (53+14+22+71)
```


##Cross Validation
```{r}
numfolds = trainControl(method = "cv", number = 10)
cpgrid = expand.grid(.cp = seq(0.01,0.5,0.01))

train(Reverse ~ Circuit + Issue + Petitioner + Respondent +LowerCourt + 
Unconst , data = train , method = "rpart" , trControl = numfolds, tuneGrid =cpgrid)  

streecv <- rpart(Reverse ~ Circuit + Issue + Petitioner + Respondent +LowerCourt + 
Unconst , data = train ,method = "class" , cp =0.01) 

predictcv <- predict(streecv , newdata = test , type ="class")
table(test$Reverse , predictcv)

(43+65) / (43+65+34+28)
```

